---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "50%"
)
```

# RT Type-1 ROC
This is the repository for the manuscript "Correcting for Unequal Variance in Signal Detection Models Using Response Time," 
available at (https://doi.org/10.31234/osf.io/cr9k6_v1).

## Unequa-variance signal detection theory analysis
The code `uvsdt.R` defines the function `fit_uvsdt_mle()` for model fitting.  
`nr_s1` and `nr_s2` are response frequency vectors for S1 (target-absent) and S2 (target present) trials, ordered from fastest-RT (or highest-confidence) Yes to fastest-RT (or highest-confidence) No responses.  
`add_constant = TRUE` adds a small value to the response frequency vectors primarily for avoiding zero-cell-related issues (default value is TRUE).

```{r example}
nr_s1 <- c(200,  360, 160, 400, 820, 1370)
nr_s2 <- c(1970, 420, 120, 170, 300, 320)

source("uvsdt.R")
f1 <- fit_uvsdt_mle(nr_s1, nr_s2, add_constant = TRUE)
f1
```

## Files
`perception` folder includes data and code for the main manuscript, where `analysis_perception` implements all the analyses reported.  
`memory` folder includes data and code for the supplementary material, where `analysis_memory` implements the relevant analyses.  



